Embedded Scalars, Preferred Readings \& Prosody: {A}n Experimental Revisit

### 2015-11-03 text/paper/reviews_2/response_letter.md

<!---Unfortunately, we do not understand in what sense the paper leaves question (ii) unresolved, according to the reviewer. To be clear on this, we wanted to get experimental evidence for preferences among putative readings, and we did. We also discuss whether these are predicted by the competing theories. We have adjusted the formulation of these conclusions according to the reviewer's well-taken suggestions in the new version (see below). We never meant to address the question how preferences are determined (and are not clear on what this should mean).-->

>Section 1: The question-answer structure of the paper
>
>It will help me to discuss the paper's contributions by taking Chemla & Spector (2011, hf. CS) as relevant background, as they also aimed to detect embedded readings in AS and ES sentences and found results that are sometimes supported but sometimes challenged by the present authors. I focus here on ES sentences, in part because AS sentences are not ideal for teasing apart "grammaticalism" from "unrestricted traditionalism", for reasons discussed in CS and elsewhere. My aim here is to identify some of the important empirical results from the current paper, and to relate them to questions (i) and (ii) above:
>
>Empirical Result (1): Like CS, but using a different method, the present authors find that embedded strengthenings are available.
>
>Consequences of (1): This result supports two of CS's claims. First, it provides further evidence for embedded strengthening (and hence, on the face of it, against Traditionalism -- pending further clarification of "typicality"), though of course it leaves open the question in (i) above. Second, ** (1) provides further support for CS's claim that the Strongest Meaning Hypothesis is probably *not* the right disambiguation principle (see note 6 of CS, and CS's section 5.5.2)**.

We are very grateful for drawing our attention to the fact that we should mention that Chemla & Spector have already discussed their data as countering the Strongest Meaning Hypothesis. We agree with this point but we believe that we are providing further evidence that is relevant for this discussion, given the doubts that were brought forth against Chemla & Spector's design and interpretation and the additional doubts that arise from issues with "silent prosody".

@@

We agree that our previous version did not make this clear enough. We reformulated relevant locations to make clear what our position is, namely (same as above):

a. we stress (even more than before) that grammaticalism qua "core theory" is compatible with our data, while traditionalism is not; 
b. still, we maintain that grammaticalism qua "core theory" is *trivially* compatible with our data, because it would not be inconsistent with any possible outcome of our experiment; 
c. the only auxiliary assumption for grammaticalism that is directly applicable to our experiment (selecting reading preferences in terms of logical strength alone) is not compatible with our data.

> Section 2: Minor comments/thoughts (feel free to ignore)
>
> A: "Exactly one" as monotonic: **The authors suggest, based on the "true" responses at Step 2, that some of their participants might have re-interpreted "exactly one" as "at least one." I'm wondering if there is a less radical way to make sense of their participants' behaviour: for what it's worth, my intuition is that there might be domain-restriction effects here.** There is exactly one uncovered bell at Step 2; thus, the sentence is literally true under a reading in which the domain of the quantifier is restricted to this one individual. I'm not exactly sure how to dissociate this suggestion from the authors', and I of course wouldn't insist that the authors do this. I raise the idea here simply for their consideration. With this in mind, in future work perhaps the authors might consider examining what would happen if Step 1 were followed instead by what is currently Step 3. The domain-restriction proposal would predict less "true" responses here because now there are two bells that are salient in the domain, but an "at least one" reading would still easily permit a "true" response here. (Note that getting rid of the current Step 2 is largely harmless, since global readings were basically absent in this paradigm.)

This is a good and interesting suggestion, but we feel that discussing this would lead us too far away from our main concerns.

### 2015-11-03 text/paper/revision_02/paper.tex
more final edits petra

Most straightforwardly, disambiguation by logical strength predicts that preferences for
readings would just mirror the entailment relations in (\ref{bsp:Entailments-AS}) and
(\ref{bsp:Entailments-GE}): for \as-sentences, weak grammaticalism predicts that local readings
are preferred over global readings which in turn are preferred over literal readings; for
\es-sentences weak grammaticalism predicts that global readings are most preferred, while
literal and local readings are not ranked with respect to
preference.\footnote{\citet{ChierchiaFox2008:The-Grammatical} consider another, more elaborate
  variant of disambiguation based on strongest meanings, but it is not necessary for purposes
  to discuss these details here.}

>>>>

Most straightforwardly, disambiguation by logical strength predicts that preferences for
readings would just mirror the entailment relations in (\ref{bsp:Entailments-AS}) and
(\ref{bsp:Entailments-GE}): for \as-sentences, grammaticalism predicts that local readings are
preferred over global readings which in turn are preferred over literal readings; for
\es-sentences grammaticalism predicts that global readings are most preferred, while literal
and local readings are not ranked with respect to
preference.\footnote{\citet{ChierchiaFox2008:The-Grammatical} consider another variant of
  disambiguation based on strongest meanings in which parses that differ in more than one
  absence/presence of silent exhaustification are incomparable. We ignore this for simplicity,
 because it matters little for the conclusions drawn from our experimental data.}
